Decoupled Fallback: A Portable Single-Pass GPU Scan

### 2025-02-27 paper.tex
#18 stab at CCS and keywords

\begin{CCSXML}
  <ccs2012>
  <concept>
  <concept_id>00000000.0000000.0000000</concept_id>
  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
  <concept_significance>500</concept_significance>
  </concept>
  <concept>
  <concept_id>00000000.00000000.00000000</concept_id>
  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
  <concept_significance>300</concept_significance>
  </concept>
  <concept>
  <concept_id>00000000.00000000.00000000</concept_id>
  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
  <concept_significance>100</concept_significance>
  </concept>
  <concept>
  <concept_id>00000000.00000000.00000000</concept_id>
  <concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
  <concept_significance>100</concept_significance>
  </concept>
  </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
\ccsdesc[300]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
\ccsdesc{Do Not Use This Code~Generate the Correct Terms for Your Paper}
\ccsdesc[100]{Do Not Use This Code~Generate the Correct Terms for Your Paper}

\keywords{Do, Not, Us, This, Code, Put, the, Correct, Terms, for,
  Your, Paper}

>>>>

\begin{CCSXML}
  <ccs2012>
  <concept>
  <concept_id>10010147.10010169.10010170.10010174</concept_id>
  <concept_desc>Computing methodologies~Massively parallel algorithms</concept_desc>
  <concept_significance>500</concept_significance>
  </concept>
  <concept>
  <concept_id>10010520.10010521.10010528</concept_id>
  <concept_desc>Computer systems organization~Parallel architectures</concept_desc>
  <concept_significance>500</concept_significance>
  </concept>
  <concept>
  <concept_id>10003752.10003753.10003761.10003762</concept_id>
  <concept_desc>Theory of computation~Parallel computing models</concept_desc>
  <concept_significance>500</concept_significance>
  </concept>
  <concept>
  <concept_id>10003752.10003753.10003761</concept_id>
  <concept_desc>Theory of computation~Concurrency</concept_desc>
  <concept_significance>500</concept_significance>
  </concept>
  <concept>
  <concept_id>10010147.10010169.10010175</concept_id>
  <concept_desc>Computing methodologies~Parallel programming languages</concept_desc>
  <concept_significance>500</concept_significance>
  </concept>
  </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computing methodologies~Massively parallel algorithms}
\ccsdesc[500]{Computer systems organization~Parallel architectures}
\ccsdesc[500]{Theory of computation~Parallel computing models}
\ccsdesc[500]{Theory of computation~Concurrency}
\ccsdesc[500]{Computing methodologies~Parallel programming languages}

\keywords{scan, parallel prefix, prefix sum, forward-progress guarantee, GPU, WGSL, decoupled fallback}
